Miniproject - Combinatorics

### 2021-12-05 Combinatorics/submission.tex
started with algebraic geometry

\section{Part III}
We even show the slightly stronger stronger statement that the implication to the second condition of Prop.\ref{prop:characterization_lym} already holds ``locally'', i.e. for each layer separately.
\begin{proposition}
    Let $P$ be a graded poset with layers $L_0, ..., L_n$ and let $0 < i \leq n$ such that
    \begin{itemize}
        \item Each element $a \in L_i$ covers the same number of elements in $L_{i - 1}$
        \item Each element $a \in L_{i - 1}$ is covered by the same number of elements in $L_i$
    \end{itemize}
    Then for each $F \subseteq L_i$ have
    \begin{equation*}
        \frac {|\partial F|} {|L_{i - 1}|} \geq \frac {|F|} {|L_i|}
    \end{equation*}
    In particular, if this is true for all $i$, then all the equivalent conditions from Prop.~\ref{prop:characterization_lym} follow.
\end{proposition}
\begin{proof}
    Assume that for all $a \in L_i$
    \begin{equation*}
        |\{ b \in L_{i - 1} \ | \ \text{$a$ covers $b$} \}| = k \in \N
    \end{equation*}
    and for all $b \in L_{i - 1}$
    \begin{equation*}
        |\{ a \in L_i \ | \ \text{$a$ covers $b$} \}| = l \in \N
    \end{equation*}
    Double-counting pairs $(a, b) \in L_i \times L_{i - 1}$ such that $a$ covers $b$ yields $k|L_i| = l|L_{i - 1}|$.
    Now consider $F \subseteq L_i$.
    Note that by definition of $\partial F$, we have for all $a \in F$ that
    \begin{equation*}
        \{ b \in \partial F \ | \ \text{$a$ covers $b$} \} = \{ b \in L_{i - 1} \ | \ \text{$a$ covers $b$} \} = \partial \{a\} \subseteq \partial F
    \end{equation*}
    Again by double-counting pairs $(a, b) \in F \times \partial F$ such that $a$ covers $b$, we find
    \begin{align*}
        k|F| =& \sum_{a \in F} k = \sum_{a \in F} |\{ b \in L_{i - 1} \ | \ \text{$a$ covers $b$} \}| = \sum_{a \in F} |\{ b \in \partial F \ | \ \text{$a$ covers $b$} \}| \\
        =& |\{ (a, b) \in F \times \partial F \ | \ \text{$a$ covers $b$} \}| = \sum_{b \in \partial F} |\{ a \in F \ | \ \text{$a$ covers $b$}\}| \\
        \leq& \sum_{b \in \partial F} |\{ a \in L_i \ | \ \text{$a$ covers $b$}\}| = \sum_{b \in \partial F} l = l |\partial F|
    \end{align*}
    Hence
    \begin{equation*}
        \frac {|\partial F|} {|L_{i - 1}|} = \frac {l |\partial F|} {l |L_{i - 1}|} \leq \frac {k |F|} {k |L_i|} = \frac {|F|} {|L_i|}
    \end{equation*}
\end{proof}

@@

    In the first case, consider
    \begin{equation*}
        \tilde{\pi} := \{ A_{jk} \ | \ j \neq s \} \cup \Bigl\{ A_{s1}, \bigcup_{2 \leq j \leq m_s} A_{sj} \Bigr\}
    \end{equation*}
    and in the second case, consider
    \begin{equation*}
        \tilde{\pi} := \{ A_{jk} \ | \ j \neq s \} \cup \Bigl\{ \bigcup_{j \leq m_s} A_{sj} \Bigr\}
    \end{equation*}
    Then $\pi_{i - 1} < \tilde{\pi} < \pi_i$ and we found a longer chain
    \begin{equation*}
        \pi_1 < ... < \pi_{i - 1} < \tilde{\pi} < \pi_i < ... < \pi_t
    \end{equation*}
    which contradicts the assumed maximality. The claim follows.
\end{proof}
\begin{proposition}
    \label{prop:partitions_recursion}
    For the number $S(m, k) := |\{ \pi \in \Pi_m \ | \ |\pi| = k\}|$ we have recursion
    \begin{equation*}
        S(m, 1) = 1 \quad \text{and} \quad S(m, k) = \sum_{n = 1}^{m - 1} {m - 1 \choose n} S(n, k - 1)
    \end{equation*}
    where $1 \leq k \leq m$.
\end{proposition}
\begin{proof}
    Use induction on $k$. 
    The base case $k = 1$ is trivial, so let $k > 1$.
    For any partition $\pi \in \Pi_m$, denote by $A(1, \pi)$ the unique set $A \in \pi$ with $1 \in A$.
    We find
    \begin{align*}
        S(m, k) =& |\{ \pi \in \Pi_m \ | \ |\pi| = k \}| = \Bigl| \bigcup_{\emptyset \neq A \subseteq [m], \ 1 \in A} \{ \pi \in \Pi_m \ | \ |\pi| = k, A(1, \pi) = A \} \Bigr| \\
        =& \sum_{\emptyset \neq A \subseteq [m], \ 1 \in A} |\{ \pi \in \Pi_m \ | \ |\pi| = k, A(1, \pi) = A \}| \\
        =& \sum_{\emptyset \neq A \subseteq [m], \ 1 \in A} |\{ \pi \in \Pi_m \ | \ |\pi \setminus \{A\}| = k - 1, A(1, \pi) = A\}| \\
        =& \sum_{\emptyset \neq A \subseteq [m], \ 1 \in A} |\{ \pi \in \Pi_{m - |A|} \ | \ |\pi| = k - 1 \}| \\
        =& \sum_{i = 1}^m \ \sum_{A \subseteq [m], \ |A| = i, \ 1 \in A} |\{ \pi \in \Pi_{m - i} \ | \ |\pi| = k - 1 \} \\
        =& \sum_{i = 1}^m {m - 1 \choose i - 1} S(m - i, k - 1) = \sum_{i = 0}^{m - 1} {m - 1 \choose m - i - 1} S(i, k - 1) \\
        =& \sum_{i = 1}^{m - 1} {m - 1 \choose i} S(i, k - 1)
    \end{align*}
    as for $k > 1$ have that $S(0, k) = 0$.
\end{proof}
\begin{example}
    Have for $m \geq 3$ that
    \begin{equation*}
        S(m, 2) = 2^{m - 1} - 1 \quad \text{and} \quad S(m, 3) = \frac 1 2 (3^{m - 1} - 2^m + 1)
    \end{equation*}

@@

    Assume not, then 
    \begin{equation*}
        r(a_i) - r(a_{i - 1}) = \sum_j a_{ij} - a_{(i - 1)j} \geq 2
    \end{equation*}
    For all $j$ we have $a_{ij} \geq a_{(i - 1)j}$ and so there is $s \leq d$ with $a_{is} - a_{(i - 1)s} \geq 2$ or there are different $r, s \leq d$ with $a_{ir} - a_{(i - 1)r}, a_{is} - a_{(i - 1)s} \geq 1$.
    In both cases, find
    \begin{equation*}
        \tilde{a} \in \mathcal{P}_{k, d} \ \text{defined by} \ \tilde{a}_j = \begin{cases}
            a_{(i - 1)j} & \text{if $j \neq s$} \\
            a_{(i - 1)j} + 1 & \text{otherwise}
        \end{cases}
    \end{equation*}
    with $a_{i - 1} < \tilde{a} < a_i$. However, this gives a longer chain
    \begin{equation*}
        a_1 < ... < a_{i - 1} < \tilde{a} < a_i < ... < a_t
    \end{equation*}
    which contradicts the assumed maximality. The claim follows.
\end{proof}
\begin{definition}
    Let $P$ be a graded poset with layers $L_0, ..., L_n$.
    A symmetric chain in $P$ is a chain $C \subseteq P$ such that there is $i \leq n/2$ with
    \begin{equation*}
        \forall 0 \leq j \leq n: \ C \cap L_j \neq \emptyset \ \Leftrightarrow \ i \leq j \leq n - i
    \end{equation*}
    A decomposition $\mathcal{C}$ of $P$ into chains is called symmetric chain decomposition, if all $C \in \mathcal{C}$ are symmetric.
\end{definition}
Note that this definition is compatible with the definition of a symmetric chain for the classical graded poset $\powerset(n)$.
\begin{proposition}
    Let $k, d \geq 1$. Then $\mathcal{P}_{k, d}$ has a symmetric chain decomposition.
\end{proposition}
\begin{proof}

\end{proof}
\begin{proposition}
    Let $M(k, d, n) := |\{ x \in \mathcal{P}_{k, d} \ | \ r(x) = n\}|$. Then for $k, d \geq 1$ we have the recurrence relation
    \begin{equation*}
        M(k, 1, n) = \begin{cases}
            1 & \text{if $0 \leq n \leq k$} \\
            0 & \text{otherwise}
        \end{cases}
        \quad \text{and} \quad
        M(k, d, n) = \sum_{i = 0}^k M(k, d - 1, n - i)
    \end{equation*}
\end{proposition}
\begin{corollary}
    Let $k, d \geq 1$. Then
    \begin{align*}
        M(k, 2, n) := \begin{cases}
            0 & \text{if $n > 2k$} \\
            k + 1 & \text{if $k < n \leq 2k$} \\
            n + 1 & \text{if $0 \leq n \leq k$} \\
            0 & \text{if $n < 0$}
        \end{cases}
    \end{align*}
    and
    \begin{align*}
        M(k, 3, n) := \begin{cases}
            0 & \text{if $n > 3k$} \\
            (k + 1)^2 & \text{if $2k < n \leq 3k$} \\
            (k + 1)(2n + 2 - k) / 2 & \text{if $k < n \leq 2k$} \\
            {n + 1 \choose 2} & \text{if $0 \leq n \leq k$} \\
            0 & \text{if $n < 0$}
        \end{cases}
    \end{align*}
\end{corollary}
\begin{proof}
    Just use the recurrence relation twice.
    The only nontrivial computation is if $k < n \leq 2k$ and $d = 3$; We find
    \begin{align*}
        &\sum_{i = 0}^k M(k, 2, n) = \sum_{i = 0}^n M(k, 2, n) = \sum_{i = 0}^{n - 2k - 1} 0 + \sum_{i = n - 2k}^{n - k - 1} (k + 1) + \sum_{i = n - k}^n (i + 1) \\
        =& (k + 1)(n - k - 1 - (n - 2k) + 1) + \frac {(n + 1)(n + 2)} 2 - \frac {(n - k)(n - k + 1)} 2 \\
        =& k(k + 1) + kn + n + 1 - \frac {k^2} 2 + \frac k 2 = \frac {(k + 1)(2n + 2 - k)} 2
    \end{align*}
\end{proof}
\end{document}

>>>>

\section{Part III}
We even show the slightly stronger stronger statement that the implication to the second condition of Prop.\ref{prop:characterization_lym} already holds ``locally'', i.e. for each layer separately.
\begin{proposition}
    \label{prop:biregular_implies_lym}
    Let $P$ be a graded poset with layers $L_0, ..., L_n$ and let $0 < i \leq n$ such that
    \begin{itemize}
        \item Each element $a \in L_i$ covers the same number of elements in $L_{i - 1}$
        \item Each element $a \in L_{i - 1}$ is covered by the same number of elements in $L_i$
    \end{itemize}
    Then for each $F \subseteq L_i$ have
    \begin{equation*}
        \frac {|\partial F|} {|L_{i - 1}|} \geq \frac {|F|} {|L_i|}
    \end{equation*}
    In particular, if this is true for all $i$, then all the equivalent conditions from Prop.~\ref{prop:characterization_lym} follow.
\end{proposition}
\begin{proof}
    Assume that for all $a \in L_i$
    \begin{equation*}
        |\{ b \in L_{i - 1} \ | \ \text{$a$ covers $b$} \}| = k \in \N
    \end{equation*}
    and for all $b \in L_{i - 1}$
    \begin{equation*}
        |\{ a \in L_i \ | \ \text{$a$ covers $b$} \}| = l \in \N
    \end{equation*}
    Double-counting pairs $(a, b) \in L_i \times L_{i - 1}$ such that $a$ covers $b$ yields $k|L_i| = l|L_{i - 1}|$.
    Now consider $F \subseteq L_i$.
    Note that by definition of $\partial F$, we have for all $a \in F$ that
    \begin{equation*}
        \{ b \in \partial F \ | \ \text{$a$ covers $b$} \} = \{ b \in L_{i - 1} \ | \ \text{$a$ covers $b$} \} = \partial \{a\} \subseteq \partial F
    \end{equation*}
    Again by double-counting pairs $(a, b) \in F \times \partial F$ such that $a$ covers $b$, we find
    \begin{align*}
        k|F| =& \sum_{a \in F} k = \sum_{a \in F} |\{ b \in L_{i - 1} \ | \ \text{$a$ covers $b$} \}| = \sum_{a \in F} |\{ b \in \partial F \ | \ \text{$a$ covers $b$} \}| \\
        =& |\{ (a, b) \in F \times \partial F \ | \ \text{$a$ covers $b$} \}| = \sum_{b \in \partial F} |\{ a \in F \ | \ \text{$a$ covers $b$}\}| \\
        \leq& \sum_{b \in \partial F} |\{ a \in L_i \ | \ \text{$a$ covers $b$}\}| = \sum_{b \in \partial F} l = l |\partial F|
    \end{align*}
    Hence
    \begin{equation*}
        \frac {|\partial F|} {|L_{i - 1}|} = \frac {l |\partial F|} {l |L_{i - 1}|} \leq \frac {k |F|} {k |L_i|} = \frac {|F|} {|L_i|}
    \end{equation*}
\end{proof}

@@

    In the first case, consider
    \begin{equation*}
        \tilde{\pi} := \{ A_{jk} \ | \ j \neq s \} \cup \Bigl\{ A_{s1}, \bigcup_{2 \leq j \leq m_s} A_{sj} \Bigr\}
    \end{equation*}
    and in the second case, consider
    \begin{equation*}
        \tilde{\pi} := \{ A_{jk} \ | \ j \neq s \} \cup \Bigl\{ \bigcup_{j \leq m_s} A_{sj} \Bigr\}
    \end{equation*}
    Then $\pi_{i - 1} < \tilde{\pi} < \pi_i$ and we found a longer chain
    \begin{equation*}
        \pi_1 < ... < \pi_{i - 1} < \tilde{\pi} < \pi_i < ... < \pi_t
    \end{equation*}
    which contradicts the assumed maximality. The claim follows.
\end{proof}
\begin{proposition}
    \label{prop:partitions_recursion}
    For the number $S(m, k) := |\{ \pi \in \Pi_m \ | \ |\pi| = k\}|$ we have recursion
    \begin{equation*}
        S(m, 1) = 1 \quad \text{and} \quad S(m, k) = \sum_{n = 1}^{m - 1} {m - 1 \choose n} S(n, k - 1)
    \end{equation*}
    where $1 \leq k \leq m$.
\end{proposition}
\begin{proof}
    Use induction on $k$. 
    The base case $k = 1$ is trivial, so let $k > 1$.
    For any partition $\pi \in \Pi_m$, denote by $A(1, \pi)$ the unique set $A \in \pi$ with $1 \in A$.
    We find
    \begin{align*}
        S(m, k) =& |\{ \pi \in \Pi_m \ | \ |\pi| = k \}| = \Bigl| \bigcup_{\emptyset \neq A \subseteq [m], \ 1 \in A} \{ \pi \in \Pi_m \ | \ |\pi| = k, A(1, \pi) = A \} \Bigr| \\
        =& \sum_{\emptyset \neq A \subseteq [m], \ 1 \in A} |\{ \pi \in \Pi_m \ | \ |\pi| = k, A(1, \pi) = A \}| \\
        =& \sum_{\emptyset \neq A \subseteq [m], \ 1 \in A} |\{ \pi \in \Pi_m \ | \ |\pi \setminus \{A\}| = k - 1, A(1, \pi) = A\}| \\
        =& \sum_{\emptyset \neq A \subseteq [m], \ 1 \in A} |\{ \pi \in \Pi_{m - |A|} \ | \ |\pi| = k - 1 \}| \\
        =& \sum_{i = 1}^m \ \sum_{A \subseteq [m], \ |A| = i, \ 1 \in A} |\{ \pi \in \Pi_{m - i} \ | \ |\pi| = k - 1 \} \\
        =& \sum_{i = 1}^m {m - 1 \choose i - 1} S(m - i, k - 1) = \sum_{i = 0}^{m - 1} {m - 1 \choose m - i - 1} S(i, k - 1) \\
        =& \sum_{i = 1}^{m - 1} {m - 1 \choose i} S(i, k - 1)
    \end{align*}
    as for $k > 1$ have that $S(0, k) = 0$.
\end{proof}
\begin{example}
    \label{ex:partitions_have_no_lym}
    Have for $m \geq 3$ that
    \begin{equation*}
        S(m, 2) = 2^{m - 1} - 1 \quad \text{and} \quad S(m, 3) = \frac 1 2 (3^{m - 1} - 2^m + 1)
    \end{equation*}

@@

    Assume not, then 
    \begin{equation*}
        r(a_i) - r(a_{i - 1}) = \sum_j a_{ij} - a_{(i - 1)j} \geq 2
    \end{equation*}
    For all $j$ we have $a_{ij} \geq a_{(i - 1)j}$ and so there is $s \leq d$ with $a_{is} - a_{(i - 1)s} \geq 2$ or there are different $r, s \leq d$ with $a_{ir} - a_{(i - 1)r}, a_{is} - a_{(i - 1)s} \geq 1$.
    In both cases, find
    \begin{equation*}
        \tilde{a} \in \mathcal{P}_{k, d} \ \text{defined by} \ \tilde{a}_j = \begin{cases}
            a_{(i - 1)j} & \text{if $j \neq s$} \\
            a_{(i - 1)j} + 1 & \text{otherwise}
        \end{cases}
    \end{equation*}
    with $a_{i - 1} < \tilde{a} < a_i$. However, this gives a longer chain
    \begin{equation*}
        a_1 < ... < a_{i - 1} < \tilde{a} < a_i < ... < a_t
    \end{equation*}
    which contradicts the assumed maximality. The claim follows.
\end{proof}
\begin{definition}
    Let $P$ be a graded poset with layers $L_0, ..., L_n$.
    A symmetric chain in $P$ is a chain $C \subseteq P$ such that there is $i \leq n/2$ with
    \begin{equation*}
        \forall 0 \leq j \leq n: \ C \cap L_j \neq \emptyset \ \Leftrightarrow \ i \leq j \leq n - i
    \end{equation*}
    A decomposition $\mathcal{C}$ of $P$ into chains is called symmetric chain decomposition, if all $C \in \mathcal{C}$ are symmetric.
\end{definition}
Note that this definition is compatible with the definition of a symmetric chain for the classical graded poset $\powerset(n)$.
\begin{proposition}
    Let $k, d \geq 1$. Then $\mathcal{P}_{k, d}$ has a symmetric chain decomposition.
\end{proposition}
\begin{proof}
    Use induction on $d$.
    The base case $d = 1$ is trivial, so assume that $d > 1$.
    By induction hypothesis, have a symmetric chain decomposition $\mathcal{C}$ of $\mathcal{P}_{k, d - 1}$.
    For some $C = \{ A_i, A_{i + 1}, ..., A_{d(k - 1) - i} \} \in \mathcal{C}, i < \frac n 2$ with $r(A_j) = j$ and $0 \leq l \leq k, n - 2i - 1$ consider now the chain
    \begin{equation*}
        \tilde{C}_l := \{ (A_{i + l}, j) \ | \ 0 \leq j \leq k - l \} \cup \{ (A_j, k - l) \ | \ i + l < j \leq d(k - 1) - (i + l) \}
    \end{equation*}
    Then $\tilde{C}_l$ is symmetric w.r.t. $i + l$, as for $i + l \leq j \leq dk - (i + l)$ we have
    \begin{align*}
        i + l \leq j \leq k + i \quad &\Rightarrow \quad (A_{i + l}, j - i - l) \in \tilde{C}_l, \\
        k + i < j \leq dk - (i + l) \quad &\Rightarrow \quad (A_{j - k}, k - l) \in \tilde{C}_l
    \end{align*}
    Clearly the $\tilde{C}_l$ are chains and disjoint.
    Hence, we find a symmetric chain decomposition
    \begin{equation*}
        \tilde{\mathcal{C}} := \Bigl\{ \tilde{C}_l \ \Bigm| \ C \in \mathcal{C} \ \text{symmetric chain w.r.t. $i$}, \ 0 \leq l \leq \min\{ k, n - 2i - 1 \} \Bigr\}
    \end{equation*}
    of $\mathcal{P}_{k, d}$.
\end{proof}
Note that for $k = 1$, this is exactly the proof that was done in the lecture to show that $\powerset(d)$ has a symmetric chain decomposition.

\section{Part VI}
First of all, in Example~\ref{ex:partitions_have_no_lym} we have already shown that the poset $\Pi_m$ does not satisfy the conditions from Prop.~\ref{prop:characterization_lym}.
Now we want to investigate whether $\mathcal{P}_{k, d}$ does. 
\begin{lemma}
    Let $A$ be a poset with two layers $L_0 = \{ u_1, ..., u_m \}, L_1 = \{ v_1, ..., v_n \}$.
    Then any of the conditions of Prop.~\ref{prop:characterization_lym} is equivalent to the following:

    There exists a matrix $A = (a_{ij}) \in \Q_{\geq 0}^{m \times n}$ such that for all $i, j$
    \begin{equation*}
        e_i^T A 1 = e_j^T A 1 \quad \text{and} \quad 1^T A e_i = 1^T A e_j
    \end{equation*}
    and $a_{ij} = 0$ whenever $u_i \not< v_j$.
\end{lemma}
This lemma does not seem super useful at first, but it gives us a way to check in time polynomial in $O(|P|)$ whether a given poset $P$ satisfies the conditions from Prop.~\ref{prop:characterization_lym}, by using an LP solver.
Note that this is not easily possible when working directly with any of the three conditions defined before.

Using this, I could check that $\mathcal{P}_{k, d}$ indeed satisfies the conditions for reasonably sized $|\mathcal{P}_{k, d}|$ (e.g. for $k, d \approx 6$).
Note that already for these ``small'' numbers, we get quite huge posets $|\mathcal{P}_{k, d}|$.
Hence, I believe that this is true for all $\mathcal{P}_{k, d}$.

My successful-looking attempt is based on the observation that elements of $\mathcal{P}_{k, d}$ ``behave similarly'' (in the sense that there is an element of the automorphism group $\mathrm{Aut}(\mathcal{P}_{k, d})$ mapping one to the other) if the have the same number of equally sized entries.
This looks promising, as the proof for $\powerset(n)$ and equivalently the proof of Prop.~\ref{prop:biregular_implies_lym} relies on the fact that all elements in one layer of $\powerset(n)$ ``behave similarly'' in this sense.

This is formalized in the next definition.
\begin{definition}
    Let $P = \mathcal{P}_{k, d}$. Then define
    \begin{equation*}
        P(n_0, ..., n_k) := \{ x \in P \ | \ |\{i \ | \ x(i) = j\}| = n_j \}
    \end{equation*}
    Further, for any subset $F \subseteq P$ write
    \begin{equation*}
        F(n_0, ..., n_k) := F \cap P(n_0, ..., n_k)
    \end{equation*}
\end{definition}
\begin{lemma}
    \label{prop:properties_n_distribution_subsets}
    Have
    \begin{equation*}
        |P(n_0, ..., n_k)| = { n_0 + ... + n_k \choose n_0 } { n_1 + ... + n_k \choose n_1 } ... {n_{k - 1} + n_k \choose n_{k - 1}} {n_k \choose n_k}
    \end{equation*}
    Further, for all $n_i \in \Z$ with $\sum n_i = d$ and all $a \in P(n_0, ..., n_k), 0 \leq \delta < k$ have
    \begin{align*}
        |\partial a \cap P(n_0, ..., n_\delta + 1, n_{\delta + 1} - 1, ..., n_k)| &= n_{\delta + 1}, \\
        |\partial^+ a \cap P(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)| &= n_\delta
    \end{align*}
    even if any of the $n_i$ are negative.
\end{lemma}

\begin{proposition}
    $\mathcal{P}_{k, d}$ satisfies the conditions of Prop.~\ref{prop:characterization_lym}.
\end{proposition}
\textit{Proof Attempt.}
Fix a layer $L_l$ with $0 < l \leq kd$.
Further, consider any subset $F \subseteq L_l$.
Now define
\begin{equation*}
    U := \{ (n_0, ..., n_k) \ | \ n_i \in \Z, \ n_0 + ... + n_k = d, \ \sum_i i n_i = l \}
\end{equation*}
and
\begin{equation*}
    V := \{ (n_0, ..., n_k) \ | \ n_i \in \Z, \ n_0 + ... + n_k = d, \ \sum_i i n_i = l - 1 \}
\end{equation*}
Note that now
\begin{align*}
    L_l = \bigsqcup_{(n_0, ..., n_k) \in U} P(n_0, ..., n_k) \quad \text{and} \quad L_{l - 1} = \bigsqcup_{(n_0, ..., n_k) \in V} P(n_0, ..., n_k)
\end{align*}
Now make $V \sqcup U$ into a bipartite graph $G = (V \sqcup U, E)$ by defining for $(m_0, ..., m_k) \in V, (n_0, ..., n_k) \in U$
\begin{align*}
    &\{ (m_0, ..., m_k), (n_0, ..., n_k) \} \in E \\
    &\Leftrightarrow \ \exists 0 \leq \delta < k: \ (n_0, ..., n_k) = (m_0, ..., m_\delta - 1, m_{\delta + 1} + 1, ..., m_k)
\end{align*}
Observe that the resulting graph is now $(k - 1)$-regular.
For $e = \{ (n_0, ..., n_k), (n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k) \} \in E$ define now
\begin{align*}
    v_F(e) := \ &\frac {|\partial \bigl(F(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)\bigr)(n_0, ..., n_k)|} {|P(n_0, ..., n_k)|} \\
    - &\frac {|F(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)|} {|P(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)|} \\
    \leq& \frac {|\partial F(n_0, ..., n_k)|} {|P(n_0, ..., n_k)|} - \frac {|F(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)|} {|P(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)|}
\end{align*}
where we define $|\emptyset|/|\emptyset| := 1$.
Now consider the graded poset $A := P(n_0, ..., n_k) \sqcup P(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)$ with two layers.
By Lemma~\ref{prop:properties_n_distribution_subsets} we see that
\begin{itemize}
    \item Each element in the bottom layer $v \in L_0(A)$ of $A$ is covered by $n_\delta$ elements
    \item Each element in the top layer $u \in L_1(A)$ of $A$ covers $n_{\delta + 1} + 1$ elements
\end{itemize}
Hence we can apply Prop.~\ref{prop:biregular_implies_lym} and see that $v_F(e) \geq 0$.
Define
\begin{equation*}
    p(n_0, ..., n_k) := \frac {|P(n_0, ..., n_k)|} {|L_{\sum in_i}|}
\end{equation*}
We know that all $v_F(e) \geq 0$ and by using the $(k - 1)$-regularity, we see
\begin{align*}
    0 \leq &\sum_{e \in E} v_F(e) p(n_0, ..., n_k) \\
    \leq &\sum_{e \in E} \left( \frac {|\partial F(n_0, ..., n_k)|} {|P(n_0, ..., n_k)|} - \frac {|F(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)|} {|P(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)|} \right) p(n_0, ..., n_k) \\
    = &(k - 1)\sum_{(n_0, ..., n_k) \in V} \frac {|\partial F(n_0, ..., n_k)|} {|P(n_0, ..., n_k)|} p(n_0, ..., n_k) \\
    - &\sum_{(n_0, ..., n_k) \in U} \frac {|F(n_0, ..., n_k)|} {|P(n_0, ..., n_k)|} \sum_{0 \leq \delta < k} p(n_0, ..., n_\delta + 1, n_{\delta + 1} - 1, ..., n_k) \\
    = &\frac {(k - 1) |\partial F|} {|L_{l - 1}|} - \sum_{(n_0, ..., n_k) \in U} \frac {|F(n_0, ..., n_k)|} {|P(n_0, ..., n_k)|} \sum_{0 \leq \delta < k} p(n_0, ..., n_\delta + 1, n_{\delta + 1} - 1, ..., n_k) \\
    = &\frac {(k - 1) |\partial F|} {|L_{l - 1}|} - \sum_{(n_0, ..., n_k) \in U} \frac {|F(n_0, ..., n_k)|} {|L_l|} \sum_{0 \leq \delta < k} \frac {(n_\delta + ... + n_k + 1)n_{\delta + 1}} {(n_\delta + 1)(n_{\delta + 1} + ... + n_k)}
\end{align*}
However, the sum
\begin{equation*}
    \sum_{0 \leq \delta < k} \frac {(n_\delta + ... + n_k + 1)n_{\delta + 1}} {(n_\delta + 1)(n_{\delta + 1} + ... + n_k)}
\end{equation*}
is not always $k - 1$, so this won't work out.

On a higher level, everything I did was to reduce the problem to the case that $F$ is a disjoint union of the $P(n_0, ..., n_k)$ which is nice to see, but does not help too much.

\begin{proposition}
    Let $M(k, d, n) := |\{ x \in \mathcal{P}_{k, d} \ | \ r(x) = n\}|$. Then for $k, d \geq 1$ we have the recurrence relation
    \begin{equation*}
        M(k, 1, n) = \begin{cases}
            1 & \text{if $0 \leq n \leq k$} \\
            0 & \text{otherwise}
        \end{cases}
        \quad \text{and} \quad
        M(k, d, n) = \sum_{i = 0}^k M(k, d - 1, n - i)
    \end{equation*}

    We also have the recurrence relation
    \begin{equation*}
        M(k, d, n) = \sum_{i = 0}^{\lfloor n/k \rfloor} {d \choose i} M(k - 1, d - i, n - ki)
    \end{equation*}
\end{proposition}
\begin{lemma}
    Let $R$ be a ring extension of $\Q$ (commutative with one). 
    For a polynomial $f \in R[X]$ there exists a unique polynomial $\Sigma f \in R[X]$ such that for all $x \in \Z, x \geq 0$ we have
    \begin{equation*}
        \Sigma f(x) = \sum_{i = 0}^x f(i)
    \end{equation*}
    Furthermore, $\Sigma$ is linear and $\deg(\Sigma f) = \deg(f) + 1$ and $\mathrm{lc}(\Sigma f) = \mathrm{lc}(f) / (\deg(f) + 1)$.
\end{lemma}
\begin{proof}
    Use induction on $\deg(f)$.
    As everything is linear, it suffices to show the claim for the monomials $X^d$.
    Define then
    \begin{equation*}
        \Sigma X^d := \frac 1 {d + 1} (X + 1)^{d + 1} - \frac 1 {d + 1} \sum_{k = 0}^{d - 1} {d + 1 \choose k} \left( \Sigma X^k \right)
    \end{equation*}
    It follows that for all $x \geq 0$ have
    \begin{align*}
        &\left( \Sigma X^d \right)(x + 1) - \left( \Sigma X^d \right)(x) \\
        =& \frac 1 {d + 1} \left( (x + 2)^{d + 1} - x^{d + 1} \right) - \frac 1 {d + 1} \sum_{k = 0}^{d - 1} {d + 1 \choose k} \left( \left( \Sigma X^k \right)(x + 1) - \left( \Sigma X^k \right)(x) \right) \\
        =& \frac 1 {d + 1} \left( -(x + 1)^{d + 1} + \sum_{k = 0}^{d + 1} {d + 1 \choose k} (x + 1)^k \right) - \frac 1 {d + 1} \sum_{k = 0}^{d - 1} {d + 1 \choose k} (x + 1)^k \\
        =& \frac 1 {d + 1} \left( \sum_{k = 0}^d {d + 1 \choose k} (x + 1)^k - \sum_{k = 0}^{d - 1} {d + 1 \choose k} (x + 1)^k \right) \\
        =& \frac 1 {d + 1} {d + 1 \choose d} (x + 1)^d = (x + 1)^d
    \end{align*}
    As this holds for infinitely many $x$, we see that $(\Sigma X^d)(X + 1) - \Sigma X^d = (X + 1)^d$ and the claim follows.
\end{proof}
\begin{example}
    Let $k, d \geq 1$. Then
    \begin{align*}
        M(k, 2, n) := \begin{cases}
            0 & \text{if $n > 2k$} \\
            2k - n + 1 & \text{if $k \leq n \leq 2k$} \\
            n + 1 & \text{if $0 \leq n \leq k$} \\
            0 & \text{if $n < 0$}
        \end{cases}
    \end{align*}
    Note that if two cases are applicable, they both yield the same value.
\end{example}
\end{document}
